---
title: "Aim 2 Results"
execute: 
  echo: false
  warning: false
  cache: false
---

```{r}
#| label: dat-read
ptrans <- function(pval, withp=FALSE){
  
  if (withp){
    if(pval>=0.001){
      pval.text <- paste0("p=",round(pval,3))
    }else{
      pval.text <- "p<0.001"
    }
    return(pval.text)
  }else{
    if(pval>=0.001){
      pval.text <- paste0(round(pval,3))
    }else{
      pval.text <- "<0.001"
    }
    return(pval.text)
  }
}

pval_star <- function(pval){
  
  stars <- ifelse(pval<0.05&pval>=0.01,"*",ifelse(pval<0.01&pval>=0.001,"**",ifelse(pval<0.001,"***","")))
  
  return(stars)
}




library(patchwork)
library(tidyverse)
library(readxl)
library(knitr)
library(lme4)
library(lmerTest)
library(irr)

### t 


# test p-value

# y <- T1_long$value
# trt <- T1_long$gender
# id <- T1_long$id

t_test_p <- function(y, trt, id){
  test <- summary(aov(y ~ trt + Error(id)))
  
  test[[2]][[1]]$"Pr(>F)"[1]
}



## compute ICC and RC and bias

# y1 <- T1intra$A
# y2 <- T1intra$B

icc_rc <- function(y1, y2, r = 3, r1 = 1){
  obj <- icc(cbind(y1, y2))
  
  icc <- str_c(round(obj$value, r), " (",
               round(obj$lbound, r), ", ",
               round(obj$ubound, r), ")")
  icc_p <- ptrans(obj$p.value, withp = TRUE)
  
  diff <- y1 - y2
  
  bias <- round(mean(diff, na.rm = TRUE), r1)
  RC <- round(1.96 * sd(diff, na.rm = TRUE), r1)
  
  str_c(bias, "|", RC, "|", icc, "|", icc_p)
  
}


# read demographic data
demo <- read_excel("data//Cardmap_demographics_short.xlsx") |> 
  janitor::clean_names() |> 
  mutate(
    id = parse_number(subj_number),
    .before = 1
  ) |> 
  select(
    !subj_number
  )

# T1 main
T1dat <- read_excel("data//T1_results_20240317_short.xlsx", 
                    na = "d") |>  
  janitor::clean_names() |> 
  rename(
    id = card_map
  )



# T2 main
T2dat <- read_excel("data//T2_results_20240317_short.xlsx", 
                    na = c("d", "nan")) |>  
  janitor::clean_names() |> 
  rename(
    id = card_map
  )

# merge demo data to T1 and take recon==DL

T1tmp <- demo |> 
  left_join(T1dat |> filter(recon == "DL"), join_by(id))


# colnames(T1tmp)

T1_long <- T1tmp |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, map, name, slice, value) 

# View(T1_long)
# merge demo data to T2 and take recon==DL ----------

T2tmp <- demo |> 
  left_join(T2dat |> filter(recon == "DL"), join_by(id))


# colnames(T1tmp)

T2_long <- T2tmp |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, map, name, slice, value) |> 
  filter(
    !is.na(map)
  )

za <- qnorm(0.975)
```



## Repeatability for DL reconstructions

<!-- use “intra-system” subjects for repeatability of sequence at same MR system for DL reconstructions for T1 Molli, T1 Smart1, T2, T2 fast (each n=15) -->

```{r}

T1intra <- T1tmp |> 
  filter(
    repeatability == "intra-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, map, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  )
# T1intra
#      id age_group gender map   name  slice       A     B
#    <dbl> <chr>     <chr>  <chr> <fct> <chr>   <dbl> <dbl>
#  1     1 30-39     Female MOLLI aha1  Slice 1  914.  907.
#  2     1 30-39     Female MOLLI aha2  Slice 1  956.  944.
#  3     1 30-39     Female MOLLI aha3  Slice 1  964.  941.
#  4     1 30-39     Female MOLLI aha4  Slice 1 1009. 1083.

# repeatability for T1



# ?icc
T2intra <- T2tmp |> 
  filter(
    repeatability == "intra-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, map, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  )

# View(T2intra)

###   T1 ----------------------------------------------------------------------
T1icc_seg <- T1intra |> 
  group_by(
    map, name
  ) |> 
  summarize(
    results = icc_rc(A, B),
    .groups = "drop"
  ) |> 
  separate_wider_delim(
    results,
    delim = "|",
    names = c("Bias", "RC", "ICC (95% CI)", "P-value")
  ) |> 
  mutate(
    across(c("RC", "Bias"), parse_number)
  )

T1icc<- T1intra |> 
  group_by(
    map
  ) |> 
  summarize(
    results = icc_rc(A, B),
    .groups = "drop"
  ) |> 
  separate_wider_delim(
    results,
    delim = "|",
    names = c("Bias", "RC", "ICC (95% CI)", "P-value")
  ) |> 
  mutate(
    across(c("RC", "Bias"), parse_number)
  )

# BA plot for T1
BAT1 <- T1intra |> 
  mutate(
    x = (A + B) / 2,
    y = (A - B)
  ) |> 
  ggplot(aes(x= x, y = y)) +
  geom_point(aes(color = slice), size = 2) +
  geom_hline(yintercept = 0, linetype = 3) +
  geom_hline(data = T1icc, aes(yintercept = Bias), linetype = 1, color = "gray40") +
  geom_hline(data = T1icc, aes(yintercept = Bias + RC), linetype = 2) +
  geom_hline(data = T1icc, aes(yintercept = Bias - RC), linetype = 2) +
  geom_text(data = T1icc, x = -Inf, y = Inf, 
            aes(label = str_c("Bias (95% CI): ", Bias, " (", 
                              Bias - RC, ", ", Bias + RC, ")")), hjust =     0, vjust = 1) + 
  scale_y_continuous("Difference", limits = c(-200, 200)) +
  scale_x_continuous("Mean") + 
  facet_wrap(~ map, scales = "free") +
  theme_bw() +
  theme(
    legend.title = element_blank()
  )


###   T2 ----------------------------------------------------------------------
T2icc_seg <- T2intra |> 
  group_by(
    map, name
  ) |> 
  summarize(
    results = icc_rc(A, B),
    .groups = "drop"
  ) |> 
  separate_wider_delim(
    results,
    delim = "|",
    names = c("Bias", "RC", "ICC (95% CI)", "P-value")
  ) |> 
  mutate(
    across(c("RC", "Bias"), parse_number)
  )


T2icc <- T2intra |> 
  group_by(
    map
  ) |> 
  summarize(
    results = icc_rc(A, B),
    .groups = "drop"
  ) |> 
  separate_wider_delim(
    results,
    delim = "|",
    names = c("Bias", "RC", "ICC (95% CI)", "P-value")
  ) |> 
  mutate(
    across(c("RC", "Bias"), parse_number)
  )
# BA plot for T2
BAT2 <- T2intra |> 
  mutate(
    x = (A + B) / 2,
    y = (A - B)
  ) |> 
  ggplot(aes(x= x, y = y)) +
  geom_point(aes(color = slice), size = 2) +
  geom_hline(yintercept = 0, linetype = 3) +
  geom_hline(data = T2icc, aes(yintercept = Bias), linetype = 1, color = "gray40") +
  geom_hline(data = T2icc, aes(yintercept = Bias + RC), linetype = 2) +
  geom_hline(data = T2icc, aes(yintercept = Bias - RC), linetype = 2) +
  geom_text(data = T2icc, x = -Inf, y = Inf, 
            aes(label = str_c("Bias (95% CI): ", Bias, " (", 
                              Bias - RC, ", ", Bias + RC, ")")), hjust =     0, vjust = 1) + 
  scale_y_continuous("Difference", limits = c(-12, 12)) +
  scale_x_continuous("Mean") + 
  facet_wrap(~ map, scales = "free") +
  theme_bw() +
  theme(
    legend.title = element_blank()
  )


```

The bias, repeatability coefficient (RC), intraclass correlation coefficient (ICC) and 95% confidence interval comparing scan A vs B are tabulated in @tbl-icc-repeat. Bland-Altman plots are shown in @fig-BA-repeat.

```{r}
#| label: fig-BA-repeat
#| fig-cap: Bland-Altman analysis of repeatability for T1 and T2
#| fig-width: 8
#| fig-height: 8

BAT1 / BAT2 + plot_layout(guides = "collect") & theme(legend.position = "top")
```


```{r}
#| label: tbl-icc-repeat
#| tbl-cap: Repeatability analysis of T1 and T2.
#| tbl-subcap:
#|   - "T1"
#|   - "T2"

T1icc_seg |> 
  kable(align = "c")

T2icc_seg |> 
  kable(align = "c")
```


## Between-system reproducibility

```{r}

# T1tmp |> 
#   filter(
#     repeatability == "intra-system"
#   ) |> View()

# T1tmp |> 
#   filter(
#     repeatability == "inter-system"
#   ) |> View()

T1inter <- T1tmp |> 
  filter(
    repeatability == "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, map, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  )
# T1inter
#      id age_group gender map   name  slice       A     B
#    <dbl> <chr>     <chr>  <chr> <fct> <chr>   <dbl> <dbl>
#  1     1 30-39     Female MOLLI aha1  Slice 1  914.  907.
#  2     1 30-39     Female MOLLI aha2  Slice 1  956.  944.
#  3     1 30-39     Female MOLLI aha3  Slice 1  964.  941.
#  4     1 30-39     Female MOLLI aha4  Slice 1 1009. 1083.

# repeatability for T1



# ?icc
T2inter <- T2tmp |> 
  filter(
    repeatability == "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, map, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  )

# View(T2inter)

###   T1 ----------------------------------------------------------------------
T1icc_inter <- T1inter |> 
  group_by(
    map
  ) |> 
  summarize(
    results = icc_rc(A, B)
  ) |> 
  separate_wider_delim(
    results,
    delim = "|",
    names = c("Bias", "RC", "ICC (95% CI)", "P-value")
  ) |> 
  mutate(
    across(c("RC", "Bias"), parse_number)
  )

# BA plot for T1
BAT1inter <- T1inter |> 
  mutate(
    x = (A + B) / 2,
    y = (A - B)
  ) |> 
  ggplot(aes(x= x, y = y)) +
  geom_point(aes(color = slice), size = 2) +
  geom_hline(yintercept = 0, linetype = 3) +
  geom_hline(data = T1icc_inter, aes(yintercept = Bias), linetype = 1, color = "gray40") +
  geom_hline(data = T1icc_inter, aes(yintercept = Bias + RC), linetype = 2) +
  geom_hline(data = T1icc_inter, aes(yintercept = Bias - RC), linetype = 2) +
  geom_text(data = T1icc_inter, x = -Inf, y = Inf, 
            aes(label = str_c("Bias (95% CI): ", Bias, " (", 
                              Bias - RC, ", ", Bias + RC, ")")), hjust =     0, vjust = 1) + 
  scale_y_continuous("Difference", limits = c(-200, 200)) +
  scale_x_continuous("Mean") + 
  facet_wrap(~ map, scales = "free") +
  theme_bw() +
  theme(
    legend.title = element_blank()
  )


###   T2 ----------------------------------------------------------------------
T2icc_inter <- T2inter |> 
  group_by(
    map
  ) |> 
  summarize(
    results = icc_rc(A, B)
  ) |> 
  separate_wider_delim(
    results,
    delim = "|",
    names = c("Bias", "RC", "ICC (95% CI)", "P-value")
  ) |> 
  mutate(
    across(c("RC", "Bias"), parse_number)
  )

# BA plot for T2
BAT2inter <- T2inter |> 
  mutate(
    x = (A + B) / 2,
    y = (A - B)
  ) |> 
  ggplot(aes(x= x, y = y)) +
  geom_point(aes(color = slice), size = 2) +
  geom_hline(yintercept = 0, linetype = 3) +
  geom_hline(data = T2icc_inter, aes(yintercept = Bias), linetype = 1, color = "gray40") +
  geom_hline(data = T2icc_inter, aes(yintercept = Bias + RC), linetype = 2) +
  geom_hline(data = T2icc_inter, aes(yintercept = Bias - RC), linetype = 2) +
  geom_text(data = T2icc_inter, x = -Inf, y = Inf, 
            aes(label = str_c("Bias (95% CI): ", Bias, " (", 
                              Bias - RC, ", ", Bias + RC, ")")), hjust =     0, vjust = 1) + 
  scale_y_continuous("Difference", limits = c(-14, 14)) +
  scale_x_continuous("Mean") + 
  facet_wrap(~ map, scales = "free") +
  theme_bw() +
  theme(
    legend.title = element_blank()
  )

```

The bias, reproducibility coefficient (RC), intraclass correlation coefficient (ICC) and 95% confidence interval comparing scan A vs B are tabulated in @tbl-icc-rep-inter-sys. Bland-Altman plots are shown in @fig-BA-rep-inter-sys.

```{r}
#| label: tbl-icc-rep-inter-sys
#| tbl-cap:  Between-system reproducibility analysis of T1 and T2.

T1icc_inter |> 
  add_row(T2icc_inter) |> 
  kable(align = "c")


```

```{r}
#| label: fig-BA-rep-inter-sys
#| fig-cap: Bland-Altman analysis of between-system reproducibility for T1 and T2
#| fig-width: 8
#| fig-height: 8

BAT1inter / BAT2inter + plot_layout(guides = "collect") & theme(legend.position = "top")
```

### Between-sequence reproducibility

<!-- use all subjects (use scan A for each subject except for the inter-system subjects. For the inter-system subjects please use the scan B) for between-sequence reproducibility 1) MOLLI DL vs SMART1 DL, 2) T2 DL vs T2fast DL. (If data from scan A is not available for intra-system subjects, feel free to use scan B data.) -->

```{r}

# prepare data for T1

T1_non_inter <- T1tmp |> 
  filter(
    repeatability != "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, map, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  ) |> 
  mutate(
    value = coalesce(A, B)
  ) 

T1_inter <- T1inter |> 
  mutate(
    value = coalesce(B, A)
  ) 

# T1 combine 
T1seq <- T1_non_inter |> 
  add_row(T1_inter) |> 
  pivot_wider(
    id_cols = c(id, name, slice),
    values_from = value,
    names_from = map
  ) |> 
  mutate(
    seq = "MOLLI vs SMART",
    .after = 1
  ) |> 
  rename(
    A = MOLLI,
    B = SMART
  )
  

# prepare data for T2

# View(T2tmp)

T2_non_inter <- T2tmp |> 
  filter(
    repeatability != "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, map, name, slice, value) |> 
  group_by(
    id, age_group, gender, scan,  map,  name
  ) |> 
  slice_head() |> ungroup() |> filter(!is.na(scan)) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  ) |> 
  mutate(
    value = coalesce(A, B)
  ) 

T2_inter <- T2inter |> 
  mutate(
    value = coalesce(B, A)
  ) 

# T1 combine 
T2seq <- T2_non_inter |> 
  add_row(T2_inter) |> 
  pivot_wider(
    id_cols = c(id, name, slice),
    values_from = value,
    names_from = map
  ) |> 
  mutate(
    seq = "T2 vs T2-fast",
    .after = 1
  ) |> 
  rename(
    A = T2,
    B = T2fast
  )


# combine T1 and T2
allseq <- T1seq |> add_row(T2seq)  


###   T1 and T2 ----------------------------------------------------------------------
allseq_icc <- allseq |> 
  group_by(
    seq
  ) |> 
  summarize(
    results = icc_rc(A, B)
  ) |> 
  separate_wider_delim(
    results,
    delim = "|",
    names = c("Bias", "RC", "ICC (95% CI)", "P-value")
  ) |> 
  mutate(
    across(c("RC", "Bias"), parse_number)
  )

# BA plot for T1
BATseq <- allseq |> 
  mutate(
    x = (A + B) / 2,
    y = (A - B)
  ) |> 
  ggplot(aes(x= x, y = y)) +
  geom_point(aes(color = slice), size = 2) +
  geom_hline(yintercept = 0, linetype = 3) +
  geom_hline(data = allseq_icc, aes(yintercept = Bias), linetype = 1, color = "gray40") +
  geom_hline(data = allseq_icc, aes(yintercept = Bias + RC), linetype = 2) +
  geom_hline(data = allseq_icc, aes(yintercept = Bias - RC), linetype = 2) +
  geom_text(data = allseq_icc, x = -Inf, y = Inf, 
            aes(label = str_c("Bias (95% CI): ", Bias, " (", 
                              Bias - RC, ", ", Bias + RC, ")")), hjust =     0, vjust = 1) + 
  scale_y_continuous("Difference") +
  scale_x_continuous("Mean") + 
  facet_wrap(~ seq, scales = "free") +
  theme_bw() +
  theme(
    legend.title = element_blank()
  )


```

The bias, reproducibility coefficient (RC), intraclass correlation coefficient (ICC) and 95% confidence interval comparing MOLLI vs SMART and T2 vs T2fast are tabulated in @tbl-icc-rep-seq. Bland-Altman plots are shown in @fig-BA-rep-seq. (Non-inter-system: priority scan A $\to$ B; inter-system: priority scan B $\to$ A.) Bias for MOLLI vs SMART is substantial: SMART values are bigger, causing lack of agreement.

```{r}
#| label: tbl-icc-rep-seq
#| tbl-cap:  Between-sequence reproducibility analysis of T1 and T2.

allseq_icc |> 
  rename(" " =  seq) |> 
  kable(align = "c")


```

```{r}
#| label: fig-BA-rep-seq
#| fig-cap: Bland-Altman analysis of between-sequence reproducibility for T1 and T2
#| fig-width: 8
#| fig-height: 4.2

BATseq + theme(legend.position = "top")
```

### Between-recon reproducibility

<!-- use all subjects (use scan A for each subject except for the inter-system subjects. For the inter-system subjects please use the scan B) for between-recon reproducibility 1) MOLLI Std vs MOLLI DL, 2) T2 Std vs T2 DL, 3) T2 DL vs T2 GE.  -->

```{r}

# T1-molli -----------------------------------------
molli <- demo |> 
  left_join(T1dat |> filter(map == "MOLLI"), join_by(id))

molli_non_inter <- molli |> 
  filter(
    repeatability != "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, recon, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  ) |> 
  mutate(
    value = coalesce(A, B)
  ) 

molli_inter <- molli |> 
  filter(
    repeatability == "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, recon, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  ) |> 
  mutate(
    value = coalesce(B, A)
  ) 



# T1 combine 
molli_all <- molli_non_inter |> 
  add_row(molli_inter) |> 
  filter(recon %in% c("Std", "DL")) |> 
  pivot_wider(
    id_cols = c(id, name, slice),
    values_from = value,
    names_from = recon
  ) |> 
  mutate(
    recon = "MOLLI: Std vs DL",
    .after = 1
  ) |> 
  rename(
    A = Std,
    B = DL
  )
  

# T2 --------------------------------

t2 <- demo |> 
  left_join(T2dat |> filter(map == "T2"), join_by(id))

t2_non_inter <- t2 |> 
  filter(
    repeatability != "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, recon, name, slice, value) |> 
  group_by(
    id, age_group, gender, scan,  recon,  name
  ) |> 
  slice_head() |> ungroup() |> filter(!is.na(scan)) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  ) |> 
  mutate(
    value = coalesce(A, B)
  ) 

t2_inter <- t2 |> 
  filter(
    repeatability == "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, recon, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  ) |> 
  mutate(
    value = coalesce(B, A)
  ) 



# T2 combine 
t2_all <- t2_non_inter |> 
  add_row(t2_inter) 

## t2: std vs DL
t2_std_dl <- t2_all |> 
  filter(recon %in% c("Std", "DL")) |> 
  pivot_wider(
    id_cols = c(id, name, slice),
    values_from = value,
    names_from = recon
  ) |> 
  mutate(
    recon = "T2: Std vs DL",
    .after = 1
  ) |> 
  rename(
    A = Std,
    B = DL
  )
  

## t2: DL vs GE
t2_dl_ge <- t2_all |> 
  filter(recon %in% c("DL", "GE")) |> 
  pivot_wider(
    id_cols = c(id, name, slice),
    values_from = value,
    names_from = recon
  ) |> 
  mutate(
    recon = "T2: DL vs GE",
    .after = 1
  ) |> 
  rename(
    A = DL,
    B = GE
  )

# View(t2_dl_ge)

recon_all <- molli_all |> 
  add_row(t2_std_dl) |> 
  add_row(t2_dl_ge) |> 
  mutate(
    recon = fct(recon)
  )



allrecon_icc <- recon_all |> 
  group_by(
    recon
  ) |> 
  summarize(
    results = icc_rc(A, B)
  ) |> 
  separate_wider_delim(
    results,
    delim = "|",
    names = c("Bias", "RC", "ICC (95% CI)", "P-value")
  ) |> 
  mutate(
    across(c("RC", "Bias"), parse_number)
  )



# BA plot for recon
BATrecon <- recon_all |> 
  mutate(
    x = (A + B) / 2,
    y = (A - B)
  ) |> 
  ggplot(aes(x= x, y = y)) +
  geom_point(aes(color = slice), size = 2) +
  geom_hline(yintercept = 0, linetype = 3) +
  geom_hline(data = allrecon_icc, aes(yintercept = Bias), linetype = 1, color = "gray40") +
  geom_hline(data = allrecon_icc, aes(yintercept = Bias + RC), linetype = 2) +
  geom_hline(data = allrecon_icc, aes(yintercept = Bias - RC), linetype = 2) +
  geom_text(data = allrecon_icc, x = -Inf, y = Inf, 
            aes(label = str_c("Bias (95% CI): ", Bias, " (", 
                              Bias - RC, ", ", Bias + RC, ")")), hjust =     0, vjust = 1) + 
  scale_y_continuous("Difference") +
  scale_x_continuous("Mean") + 
  facet_wrap(~ recon, scales = "free") +
  theme_bw() +
  theme(
    legend.title = element_blank()
  )

```

The bias, reproducibility coefficient (RC), intraclass correlation coefficient (ICC) and 95% confidence interval comparing MOLLI: Std vs DL, T2: Std vs DL, and T2: DL vs GE are tabulated in @tbl-icc-rep-recon. Bland-Altman plots are shown in @fig-BA-rep-recon. (Non-inter-system: priority scan A $\to$ B; inter-system: priority scan B $\to$ A.) There is strong agreement within the three pairs of comparisons.

```{r}
#| label: tbl-icc-rep-recon
#| tbl-cap:  Between-recon reproducibility analysis of T1 and T2.

allrecon_icc  |> 
  rename(" " =  recon) |> 
  kable(align = "c")


```

```{r}
#| label: fig-BA-rep-recon
#| fig-cap: Bland-Altman analysis of between-recon reproducibility for T1 and T2
#| fig-width: 8
#| fig-height: 3.5

BATrecon + theme(legend.position = "top")
```

### Between-reader reproducibility

<!-- for between-reader reproducibility, use subjects from the two “interreader” tables and compare them to the ones in the main tables. Use MOLLI DL and T2 DL data only. Readers were “RVS” and “AF”. -->

```{r}
## read in reader data
## T1 -------------------------------------------------------------------
T1reader <- read_excel("data//T1_results_interreader_20240317_short.xlsx",
                       na = c("d", "nan")) |>  
  janitor::clean_names() |> 
  rename(
    id = card_map
  )

# str(T1reader)
# str(T1dat)

T1readstmp <- T1dat |> filter(map == "MOLLI", recon == "DL") |> 
  add_row(T1reader)
  
T1reads_df <- demo |> 
  left_join(T1readstmp, join_by(id))  


T1reads_non_inter <- T1reads_df |> 
  filter(
    repeatability != "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, reader, map, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  ) |> 
  mutate(
    value = coalesce(A, B)
  ) |> 
  select(
    !c(A, B)
  ) |> 
  pivot_wider(
    values_from = value,
    names_from = reader
  ) |> 
  filter(
    !is.na(AF) & !is.na(RVS)
  )


T1reads_inter <- T1reads_df |> 
  filter(
    repeatability == "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, reader, map, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  ) |> 
  mutate(
    value = coalesce(B, A)
  ) |> 
  select(
    !c(A, B)
  ) |> 
  pivot_wider(
    values_from = value,
    names_from = reader
  ) |> 
  filter(
    !is.na(AF) & !is.na(RVS)
  )

T1reads <- T1reads_non_inter |> 
  add_row(
    T1reads_inter
  ) 
  
  
## read in reader data
## T2 -------------------------------------------------------------------
T2reader <- read_excel("data//T2_results_interreader_20240317_short.xlsx",
                       na = c("d", "nan")) |>  
  janitor::clean_names() |> 
  rename(
    id = card_map
  )

# str(T2reader)
# str(T2dat)

T2readstmp <- T2dat |> filter(map == "T2", recon == "DL") |> 
  add_row(T2reader)
  
T2reads_df <- demo |> 
  left_join(T2readstmp, join_by(id))  


T2reads_non_inter <- T2reads_df |> 
  filter(
    repeatability != "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, reader, map, name, slice, value) |> 
  group_by(
    id, age_group, gender, scan,  reader, map,   name
  ) |> 
  slice_head() |> ungroup() |> filter(!is.na(scan)) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  ) |> 
  mutate(
    value = coalesce(A, B)
  ) |> 
  select(
    !c(A, B)
  ) |> 
  pivot_wider(
    values_from = value,
    names_from = reader
  ) |> 
  filter(
    !is.na(AF) & !is.na(RVS)
  )


T2reads_inter <- T2reads_df |> 
  filter(
    repeatability == "inter-system"
  ) |> 
  pivot_longer(
    c(aha1:aha16,sept_1_mean, sept_2_mean, sept_3_mean),
    values_to = "value",
    names_to = "name"
  ) |> 
  mutate(
    name = fct(name),
    slice = case_when(
      name %in% c(str_c("aha", 1:6), "sept_1_mean") ~ "Slice 1",
      name %in% c(str_c("aha", 7:12), "sept_2_mean") ~ "Slice 2",
      name %in% c(str_c("aha", 13:16), "sept_3_mean") ~ "Slice 3"
    )
  ) |> 
  select(id, age_group, gender, scan, reader, map, name, slice, value) |> 
  pivot_wider(
    names_from = scan,
    values_from = value
  ) |> 
  mutate(
    value = coalesce(B, A)
  ) |> 
  select(
    !c(A, B)
  ) |> 
  pivot_wider(
    values_from = value,
    names_from = reader
  ) |> 
  filter(
    !is.na(AF) & !is.na(RVS)
  )

T2reads <- T2reads_non_inter |> 
  add_row(
    T2reads_inter
  ) 

## combine MOLLI and T2
all_reads <- T1reads |> 
  add_row(
    T2reads
  )

all_reads_icc <- all_reads |> 
  group_by(
    map
  ) |> 
  summarize(
    results = icc_rc(RVS, AF)
  ) |> 
  separate_wider_delim(
    results,
    delim = "|",
    names = c("Bias", "RC", "ICC (95% CI)", "P-value")
  ) |> 
  mutate(
    across(c("RC", "Bias"), parse_number)
  )



# BA plot for recon
BATreads <- all_reads |> 
  mutate(
    x = (RVS + AF) / 2,
    y = (RVS - AF)
  ) |> 
  ggplot(aes(x= x, y = y)) +
  geom_point(aes(color = slice), size = 2) +
  geom_hline(yintercept = 0, linetype = 3) +
  geom_hline(data = all_reads_icc, aes(yintercept = Bias), linetype = 1, color = "gray40") +
  geom_hline(data = all_reads_icc, aes(yintercept = Bias + RC), linetype = 2) +
  geom_hline(data = all_reads_icc, aes(yintercept = Bias - RC), linetype = 2) +
  geom_text(data = all_reads_icc, x = -Inf, y = Inf, 
            aes(label = str_c("Bias (95% CI): ", Bias, " (", 
                              Bias - RC, ", ", Bias + RC, ")")), hjust =     0, vjust = 1) + 
  scale_y_continuous("Difference") +
  scale_x_continuous("Mean") + 
  facet_wrap(~ map, scales = "free") +
  theme_bw() +
  theme(
    legend.title = element_blank()
  )


```

The bias, reproducibility coefficient (RC), intraclass correlation coefficient (ICC) and 95% confidence interval comparing RVS vs AF for MOLLI and T2 are tabulated in @tbl-icc-rep-reads. Bland-Altman plots are shown in @fig-BA-rep-reads. (Non-inter-system: priority scan A $\to$ B; inter-system: priority scan B $\to$ A.) The inter-reader agreement is strong.

```{r}
#| label: tbl-icc-rep-reads
#| tbl-cap:  Between-reader (RVS vs AF) reproducibility analysis of MOLLI and T2.

all_reads_icc  |> 
  rename(" " =  map) |> 
  kable(align = "c")


```

```{r}
#| label: fig-BA-rep-reads
#| fig-cap: Bland-Altman analysis of between-reader (RVS vs AF) reproducibility for MOLLI and T2
#| fig-width: 8
#| fig-height: 4.2

BATreads+ theme(legend.position = "top")
```
